On the formation of H$\alpha$ line emission around classical T Tauri star: the disc-wind-magnetosphere hybrid models

### 2006-01-29 TTau_Halpha/kurosawa.tex
minor change in the caption in the apendix.  (rk)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@644 25464f21-6099-402c-b30a-640f1d40d38b

  \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
  $\dot{M}_{\mathrm{acc}} =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr{-1}}$. 
  Profiles are presented
  for inclinations of $10^\circ$ (top figure), $55^\circ$ (middle figure), and $80^\circ$ (bottom figure).
  For each inclination, 12 profiles are given, for three different values of the wind temperature, and four
  different values of the wind acceleration parameter $\beta$.}

>>>>

  \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid
  model with $\dot{M}_{\mathrm{acc}}
  =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr{-1}}$.
  Profiles are presented for inclinations of $10^\circ$ (top figure),
  $55^\circ$ (middle figure), and $80^\circ$ (bottom figure).  For
  each inclination, 12 profiles are given, for three different values
  of the wind temperature, and four different values of the wind
  acceleration parameter $\beta$. The contribution of the
  magnetosphere can be judged from the profiles computed with the
  magnetosphere only (dotted lines).}
